Ethereum: Un Registro Generico delle Transazioni Sicuro e Decentralizzato \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-01-21 Paper.tex
Update Paper.tex

A transaction (formally, $T$) is a single cryptographically-signed instruction constructed by an actor externally to the scope of Ethereum. While is assumed that the ultimate external actor will be human in nature, software tools will be used in its construction and dissemination\footnote{Notably, such `tools' could ultimately become so causally removed from their human-based initiation---or humans may become so causally-neutral---that there could be a point at which they rightly be considered autonomous agents. \eg contracts may offer bounties to humans for being sent transactions to initiate their execution.}. There are two types of transactions: those which result in message calls and those which result in the creation of new accounts with associated code (known informally as `contract creation'). Both types specify a number of common fields:

\begin{description}
\item[nonce] A scalar value equal to the number of transactions sent by the sender; formally $T_n$.
\item[gasPrice] A scalar value equal to the number of Wei to be paid per unit of \textit{gas} for all computation costs incurred as a result of the execution of this transaction; formally $T_p$.
\item[gasLimit] A scalar value equal to the maximum amount of gas that should be used in executing this transaction. This is paid up-front, before any computation is done and may not be increased later; formally $T_g$.
\item[to] The 160-bit address of the message call's recipient or, for a contract creation transaction, $\varnothing$, used here to denote the only member of $\mathbb{B}_0$ ; formally $T_t$.
\item[value] A scalar value equal to the number of Wei to be transferred to the message call's recipient or, in the case of contract creation, as an endowment to the newly created account; formally $T_v$.
\item[v, r, s] Values corresponding to the signature of the transaction and used to determine the sender of the transaction; formally $T_w$, $T_r$ and $T_s$. This is expanded in Appendix \ref{app:signing}.
\end{description}

>>>>

Una transazione (formalmente, $T$) è una singola instruzione, firmata crittograficamente dall'esterno verso l'ambiente di Ethereum. Mentre si presume che l'ultimo attore esterno sarà un essere umano, gli strumenti software saranno impiegati nella sua propria costruzione e diffusione\footnote{Notably, come `strumenti' potrebbero alla fine diventare così semplici da non necessitare l'iniziativa dell'essere umano--o gli umani possono diventare occanasionalmente imparziali---che ci potrebbe assere un punto che ci potrebbe essere un punto in cui essi potrebbero giustamente essere considerati agenti autonomi. \eg i contratti possono offire ricompense agli umani per al fine di inviare transazioni per iniziare la loro esecuzione.}. Ci sono due tipi di transazioni: quelle che danno luogo a chiamate di messaggi e quelle che derivano dalla creazione di nuovi account con il codice associato (conosciuto informalmente come `creazione del contratto'). Entrambi i tipi specificano un numero di campi in comune:

\begin{description}
\item[nonce] Un valore scalare equivale al numero delle transazioni inviate dal mittente; formalmente $T_n$.
\item[gasPrice] Un valore scalare equiale al numero di Wei da pagare per unità di \textit{gas} per tutti i costi computazionali occorsi come risultato dell'esecuzione di questa transazione; formalmente $T_p$.
\item[gasLimit] A scalar value equal to the maximum amount of gas that should be used in executing this transaction. This is paid up-front, before any computation is done and may not be increased later; formally $T_g$.
\item[to] The 160-bit address of the message call's recipient or, for a contract creation transaction, $\varnothing$, used here to denote the only member of $\mathbb{B}_0$ ; formally $T_t$.
\item[value] A scalar value equal to the number of Wei to be transferred to the message call's recipient or, in the case of contract creation, as an endowment to the newly created account; formally $T_v$.
\item[v, r, s] Values corresponding to the signature of the transaction and used to determine the sender of the transaction; formally $T_w$, $T_r$ and $T_s$. This is expanded in Appendix \ref{app:signing}.
\end{description}
